Ensemble Stability of Biological Networks

### 2014-09-26 tex/figures.tex
add max/min robustness graphs to 3D plot

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=1.0\columnwidth]{fig/combinedfigs.pdf}
\caption{{\bf Characterization of stability and robustness according to properties of system structure} (A) Stability versus connectivity, (B) robustness versus connectivity, (C) robustness versus number of cycles, (D) robustness versus hierarchy%, (E) robustness versus number of cycles and connectivity, and (F) robustness versus graph edit distance and connectivity
 for three component systems.
}
\label{fig:combined}
\end{figure}

% Figure translations
% apstab3x3 4 -> A
% stab3x3 6 -> B
% cycle3x3 7 -> C
% New -> D
% connectcycle3D3x3 5 -> E
% New -> F

% \begin{figure}[!ht]
% \centering
% \noindent\includegraphics[width=0.8\columnwidth]{fig/apstab3x3.pdf}
% \caption{{\bf Plot of stability versus connectivity for three component systems.} }
% \label{fig:apstab3x3}
% \end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.7\columnwidth]{fig/connectcycle3D3x3.pdf}
\caption{{\bf Stability to perturbations versus number of cycles and connectivity for three component systems.} }
\label{fig:connectcycle3D3x3}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.7\columnwidth]{fig/connectdist3D3x3.pdf}
\caption{{\bf Robustness versus hierarchy and connectivity for three component systems.} }
\label{fig:connectdist3D3x3}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.9\columnwidth]{fig/robustnesssymmetries.pdf}
\caption{{\bf Example symmetries of robustness.} In this example, the connected component sizes are fixed at $\{2,1,1\}$ with a total of $3$ links between them. Red arrows correspond to transformations like \ref{fig:hiertransformations}A where SCCs are swapped whereas purple arrows correspond to transformations like \ref{fig:hiertransformations}B where links are moved between nodes within a SCC.}
\label{fig:robustnesssymmetries}
\end{figure}

% \begin{figure}[!ht]
% \centering
% \noindent\includegraphics[width=0.8\columnwidth]{fig/stab3x3.pdf}
% \caption{{\bf Plot of stability to perturbations versus connectivity for three component systems.} }
% \label{fig:stab3x3}
% \end{figure}

% \begin{figure}[!ht]
% \centering
% \noindent\includegraphics[width=0.8\columnwidth]{fig/cycle3x3.pdf}
% \caption{{\bf Plot of stability to perturbations versus number of cycles for three component systems.} }
% \label{fig:cycle3x3}
% \end{figure}

>>>>

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=1.0\columnwidth]{fig/combinedfigs.pdf}
\caption{{\bf Characterization of stability and robustness according to properties of system structure} (A) Stability versus connectivity, (B) robustness versus connectivity, (C) robustness versus number of cycles, (D) robustness versus hierarchy for three component systems.
}
\label{fig:combined}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.8\columnwidth]{fig/connectcycle3D3x3.pdf}
\caption{{\bf Robustness versus number of cycles and connectivity for three component systems.} Each point represents the average robustness of all graphs having a given number of cycles and connectivity.}
\label{fig:connectcycle3D3x3}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.8\columnwidth]{fig/connectdist3D3x3.pdf}
\caption{{\bf Robustness versus hierarchy and connectivity for three component systems.} Each point represents the average robustness of all graphs having a given hierarchy and connectivity.}
\label{fig:connectdist3D3x3}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.9\columnwidth]{fig/robustnesssymmetries.pdf}
\caption{{\bf Example symmetries of robustness.} In this example, the connected component sizes are fixed at $\{2,1,1\}$ with a total of $3$ links between them. Red arrows correspond to transformations like \ref{fig:hiertransformations}A where SCCs are swapped whereas purple arrows correspond to transformations like \ref{fig:hiertransformations}B where links are moved between nodes within a SCC. (A) shows all underlying graphs while (B) shows the number of nodes in each SCC and the number of links between the SCCs.}
\label{fig:robustnesssymmetries}
\end{figure}
